Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-09 Paperfolder/Paperfolder.Rmd
updated AF description in results section

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women. Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among either sex.

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had lower hazard of dying from total stroke in crude models. Chances that the posterior HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and more than 94.6% in women. However, lower hazard was observed to remain after age or multivariable adjustment only in men. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted HRs for daily male consumers of milk was 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior HRs that was distributed with mean (sd) of 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had 78.0% of chance that their HRs could be lower than 1.

Posterior distributions of HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models. In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 26%-37% lower hazard of dying from cerebral infarction compared with men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). We were more than 95.7% sure that these posterior HRs could be lower than 1. No associations were observed between milk intake and hazard of cerebral infarction among women.

>>>>

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women. Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among both sex.

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had lower hazard and slower speed of dying from total stroke in crude models. Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.88 (sd = 0.04; 95% CrI: 0.80, 0.96) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and more than 94.6% in women. However, lower hazard and speed was observed to remain after age or multivariable adjustment only in daily male milk consumers. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that was distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had 78.0% of chance that their HRs could be smaller than 1.

Posterior distributions of AFs and HRs for mortality from hemorrhagic stroke were found to contain the null value for either men or women among all fitted models. In contrast, men who had milk intake frequency higher than 1-2 times/week were found to be associated with averagely 17%-20% slower velocity or 28%-39% lower hazard of dying from cerebral infarction compared against men who never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). We were more than 97.5% sure that these posterior HRs were distributed below the null value. No apparent associations were observed between milk intake and hazard of cerebral infarction among women.

### 2020-07-09 Paperfolder/Paperfolder.tex
updated AF description in results section

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
chose ``never'' as their milk intake frequency at baseline, milk
drinkers were less likely to be a current smoker or a daily alcohol
consumer in both men and women. Furthermore, people consumed milk more
than 1-2 times/month were more likely to be a daily consumers of
vegetable, fruit as well as coffee, and more likely to join exercise
more than 1 hour/week among either sex.

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had lower hazard of dying from total stroke in
crude models. Chances that the posterior HRs were estimated to be lower
than 1 for those who had at least 1-2 times/month was higher than 86.5\%
in men and more than 94.6\% in women. However, lower hazard was observed
to remain after age or multivariable adjustment only in men.
Specifically, the mean (sd; 95\% CrI) of posterior
multivariable-adjusted HRs for daily male consumers of milk was 0.80 (sd
= 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to be smaller
than the null value (=1). Daily female milk consumers had posterior HRs
that was distributed with mean (sd) of 0.95 (sd = 0.12; 95\% CrI: 0.80,
1.17) which had 78.0\% of chance that their HRs could be lower than 1.

Posterior distributions of HRs for mortality from hemorrhagic stroke
were found to contain the null value for either men or women among all
fitted models. In contrast, men who had milk intake frequency higher
than 1-2 times/week were found to be associated with averagely 26\%-37\%
lower hazard of dying from cerebral infarction compared with men who
never drank milk (Model 2 in \textbf{Table \ref{tab:tab2}}). We were
more than 95.7\% sure that these posterior HRs could be lower than 1. No
associations were observed between milk intake and hazard of cerebral
infarction among women.

@@

>>>>

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
chose ``never'' as their milk intake frequency at baseline, milk
drinkers were less likely to be a current smoker or a daily alcohol
consumer in both men and women. Furthermore, people consumed milk more
than 1-2 times/month were more likely to be a daily consumers of
vegetable, fruit as well as coffee, and more likely to join exercise
more than 1 hour/week among both sex.

Detailed results from the Bayesian survival models (crude, age-adjusted
and multivariable adjusted) according to the frequency of milk intake
separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and
\textbf{Table \ref{tab:tab3}} (women). Compared to those who never had
milk, both men and women had lower hazard and slower speed of dying from
total stroke in crude models. Velocities that milk consumers dying from
stroke is slower by a crude acceleration factor (AF) between 0.79 (sd =
0.05; 95\% CrI: 0.74, 0.90) and 0.88 (sd = 0.04; 95\% CrI: 0.80, 0.96)
compared with non-consumers. Chances that the posterior crude HRs were
estimated to be lower than 1 for those who had at least 1-2 times/month
was higher than 86.5\% in men and more than 94.6\% in women. However,
lower hazard and speed was observed to remain after age or multivariable
adjustment only in daily male milk consumers. Specifically, the mean
(sd; 95\% CrI) of posterior multivariable-adjusted AF and HR for daily
male consumers of milk were 0.88 (sd = 0.05; 95\% CrI: 0.81, 0.96) and
0.80 (sd = 0.07; 95\% CrI: 0.69, 0.93) with a probability of 99.0\% to
be smaller than the null value (=1). Daily female milk consumers had
posterior AFs and HRs that was distributed with means of 0.97 (sd =
0.09; 95\% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95\% CrI: 0.80, 1.17)
which had 78.0\% of chance that their HRs could be smaller than 1.

Posterior distributions of AFs and HRs for mortality from hemorrhagic
stroke were found to contain the null value for either men or women
among all fitted models. In contrast, men who had milk intake frequency
higher than 1-2 times/week were found to be associated with averagely
17\%-20\% slower velocity or 28\%-39\% lower hazard of dying from
cerebral infarction compared against men who never drank milk (Model 2
in \textbf{Table \ref{tab:tab2}}). We were more than 97.5\% sure that
these posterior HRs were distributed below the null value. No apparent
associations were observed between milk intake and hazard of cerebral
infarction among women.

@@

\begin{itemize}
\tightlist
\item
\end{itemize}
